Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-19 Corrected_version.tex
correction numérique
final correction manu

We think that some of our results can have an interest for the 
development and  use of such methods in research or industrial codes with complex non linear 
physics   on unstructured meshes.
Indeed for such codes  cell-centered Finite Volume schemes %well adapted
are a natural solution in terms of  data structure.
The point is the following: the scheme studied in this work
is the only cell-centered  one  we know in 2D 
to compute
the solutions of problems which admit  diffusion limits in certain regimes and for which it is possible to prove the AP property.
Since the structure of this cell-centered scheme is nodal based, it strongly questions the ability
of standard Finite Volume methods with edge-based fluxes to recover asymptotic diffusion regimes.
As demonstrated in this work, nodal based Finite Volume techniques do not suffer from this drawback.

@@

To illustrate the theory and have a more quantitative version of the error estimates
studied in this work, we consider the academic square $\Omega=[0,1]^2$ and discretize the hyperbolic heat equation
of a mesh made with random quads. 
A random quad mesh is made of quads where the vertices are moved
randomly around their initial position, by a factor between 10\% and 30\%.
We use the fully implicit time discretization version of the 2D scheme
detailed in this work. The solution of the linear systems is computed via
an iterative GMRES algorithm, which converges smoothly in our numerical experiments.
The reference analytical solution used in our tests is designed by separation of variables.
A solution of (\ref{eq:mod1}) is
$$
p= f+\frac{\eps^2}\sigma \partial_t f
\mbox{ and }
\mathbf u= -\frac\eps \sigma \nabla f,
$$
with $f$ solution of 
$
\partial_t f +\frac{\eps^2}\sigma \partial_t^2 f -\frac1\sigma \Delta f=0$.
We add periodic boundary conditions and consider
$$
f(t,x,y)=\alpha(t)\cos (\pi x ))\cos( \pi y ).
$$
The function $\alpha$ is determined as the solution of
$$
\alpha'(t)+ \frac{\eps^2}\sigma\alpha''(t)+\frac{2\pi}\sigma \alpha=0
$$
whith $\alpha'(0)=0$ and $\alpha(0)=1$.
For small $\eps$, which is the case we are interested in, the solution is computed as follows.
First determine 
$$
\lambda_1=-
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } +1\right)
}{2 \eps^2  }
\mbox{ and }
\lambda_2=
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } -1\right)
}{2 \eps^2  }.
$$
Then 
$$
\alpha(t)=\frac{\lambda_2}{\lambda_2-\lambda_1}e^{\lambda_2 t  }
-
\frac{\lambda_1}{\lambda_2-\lambda_1}e^{\lambda_1 t  }
$$
from which $p(t)$ and $\mathbf u(t)$ are easily recovered.

@@

\bibitem{TAHO} D. Aregba, M. Briani, R. Natalini, Time Asymptotic High Order Schemes for Dissipative BGK Hyperbolic Systems, arXiv:1207.6279.

@@

>>>>

We think that some of our results can have an interest for the 
development and  use of such methods in research or industrial codes with complex non linear 
physics   on unstructured meshes.
Indeed for such codes  cell-centered Finite Volume schemes %well adapted
are a natural solution in terms of  data structure.
The point is the following: the scheme studied in this work
is the only cell-centered  one  we know in 2D 
to compute
the solutions of problems which admit  diffusion limits in certain regimes and for which it is possible to prove the AP property.
Since the structure of this cell-centered scheme is nodal based, it strongly questions the ability
of standard Finite Volume methods with edge-based fluxes to recover asymptotic diffusion regimes.
As demonstrated in this work, nodal based Finite Volume techniques do not suffer from this drawback. For linear wave equation the nodal scheme can be understand as some 1D Riemann problem written in some direction around each node. This a approximation of the 2D Riemann problem \cite{2Driemann}.

@@

To illustrate the theory and have a more quantitative version of the error estimates
studied in this work, we consider the academic square $\Omega=[0,1]^2$ and discretize the hyperbolic heat equation
of a mesh made with random quads. 
A random quad mesh is made of quads where the vertices are moved
randomly around their initial position, by a factor between 10\% and 30\%.
We use the fully implicit time discretization version of the 2D scheme
detailed in this work. The solution of the linear systems is computed via
an iterative GMRES algorithm, which converges smoothly in our numerical experiments.
The reference analytical solution used in our tests is designed by separation of variables.
A solution of (\ref{eq:mod1}) is
$$
p= f+\frac{\eps^2}\sigma \partial_t f
\mbox{ and }
\mathbf u= -\frac\eps \sigma \nabla f,
$$
with $f$ solution of 
$
\partial_t f +\frac{\eps^2}\sigma \partial_t^2 f -\frac1\sigma \Delta f=0$.
We add periodic boundary conditions and consider
$$
f(t,x,y)=\alpha(t)\cos (\pi x ))\cos( \pi y ).
$$
The function $\alpha$ is determined as the solution of
$$
\alpha'(t)+ \frac{\eps^2}\sigma\alpha''(t)+\frac{2\pi}\sigma \alpha=0
$$
whith $\alpha'(0)=0$ and $\alpha(0)=1$.
For small $\eps$, which is the case we are interested in, the solution is computed as follows.
First determine 
$$
\lambda_1=-
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } +1\right)
}{2 \eps^2  }
\mbox{ and }
\lambda_2=
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } -1\right)
}{2 \eps^2  }.
$$
Then 
$$
\alpha(t)=\frac{\lambda_2}{\lambda_2-\lambda_1}e^{\lambda_1 t  }
-
\frac{\lambda_1}{\lambda_2-\lambda_1}e^{\lambda_2 t  }
$$
from which $p(t)$ and $\mathbf u(t)$ are easily recovered.

@@

\bibitem{TAHO} D. Aregba, M. Briani, R. Natalini, \emph{Time Asymptotic High Order Schemes for Dissipative BGK Hyperbolic Systems}, arXiv:1207.6279.

@@

\bibitem{2DRiemann}  L. Gosse, \emph{A two-dimensional version of the Godunov scheme for scalar balance laws}. SIAM J. Numer. Anal. 52 (2014) 626?652.
